Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-02-24 ribose-paper.RMD
updates

The purpose of this investigation was to test the hypothesis that glucose supplementation in connection to<!-- during? --> RT would increase markers of ribosomal abundance following five RT sessions. Secondly we aimed to describe the association between UBF and total RNA abundance in human skeletal muscle.   
<!-- We should maybe add a line or two about the rational here -->

>>>>

The purpose of this investigation was to test the hypothesis that glucose supplementation before and after<!-- during? before and after would be more precise --> RT would increase markers of ribosomal abundance following five RT sessions. Secondly we aimed to describe the association between UBF and total RNA abundance in human skeletal muscle.   
<!-- We should maybe add a line or two about the rational here -->
